From heartbeat to data – Using wearable fitness trackers as an affordable approach to assess teacher stress

### 2024-09-25 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
nochmal quasi final

The teaching profession is one of the most stressful professions, with teachers facing a host of stressors during their everyday work [@smith2000; @herman2020; @schult2014belastet]. To better understand mechanisms in teacher stress, there is a growing research interest in physiological measures such as heart rate (HR) as online measures of teachers’ stress during teaching [@karner2021teachers; @wettstein2020ambulatory]. For example, it has been shown that teacher-centered activities and typical classroom-related stressors increase teacher HR during teaching activities [@sperka1995; @scheuch1997psychophysische; @donker2018; @junker2021; @huang2022class]. However, previous studies have often relied on expensive and obtrusive electrocardiographs (ECG). Modern fitness trackers represent a non-invasive and convenient alternative. [@ferguson2015]

@@

Physiologically, HR is regulated by the sympathetic and parasympathetic nervous systems [@pham2021]. An increase in sympathetic activity results in HR being sped up (“fight or flight” response) [@taelman2009influence]; whereas an increase in parasympathetic activity results in HR being slowed down (“rest and digest” response) [@battipaglia2015]. Stress or mental and physical strain directly increases HR [@custodis2014heart; @sachs2014]. Therefore, an increase in HR can be regarded as an indicator of increasing stress, and a decrease as an indicator of relaxation and ease [@kyriacou1978]. Thus, fitness trackers offer low-cost and unobtrusive access to psychological stress data.

@@

```{=latex}
\captionsetup[figure]{
    labelfont=bf,         % Figure label bold (not italic)
    parskip=12pt,
    labelsep=newline,      % Period after Figure label
    textfont=it,          % Italic font for the caption text
    font=small,           % Smaller font size for APA style
    justification=justified, % Left-justified captions, as per APA guidelines
    singlelinecheck=false % Avoid centering if the caption is single-line
}

\captionsetup[table]{
    labelfont=bf,         % Figure label bold (not italic)
    parskip=12pt,
    labelsep=newline,      % Period after Figure label
    textfont=it,          % Italic font for the caption text
    font=small,           % Smaller font size for APA style
    justification=justified, % Left-justified captions, as per APA guidelines
    singlelinecheck=false % Avoid centering if the caption is single-line
}

\begin{figure}[htbp]
  \caption{A model of teacher stress (adapted from van Dick 2006, p.37, modified by the authors)}
  \centering
  \includegraphics[width=1\textwidth]{images/Model_Teacher_Stress_adapted_new.pdf}
  \label{fig.1}
\end{figure}
```

Fig. 1 shows, in a simplified way, how classroom events affect teachers’ stress level, according to the adaptation of the Lazarus model to teacher stress proposed by @van2006stress: When potential stressors (e.g., classroom disruptions) occur during teaching (1), teachers intuitively judge how disruptive the event is in a primary appraisal (2). If potential stressors are judged as threatening, i.e., as actual stressors (3), teachers consider whether they have sufficient resources for coping with the stressors (4). Teachers utilize these resources in trying to cope with the stressors, e.g., by employing classroom management strategies (5). In cases when coping fails, stress ensues, often accompanied by physiological reactions like increased HR (6). As part of the coping process, and dependent on its outcomes, teachers re-evaluate the stressor (7).

As shown in Fig. 1, teachers’ primary and secondary appraisal as well as coping attempts are influenced by professional experience. As professional experience grows, teachers develop cognitive scripts for managing classroom events, resulting in more complex and problem-focused classroom management skills [@wolff2021classroom], and thus more effective coping and less stress. Empirically, classroom management skills and problem-focused coping styles are linked to fewer instances of emotional exhaustion [@maslach2001job; @clunies2008self]. Novices in the teaching profession, on the other hand, face considerable stress and often feel overwhelmed by the demands of teaching [@ophardt2017klassenmanagement; @wolff2015keeping; @klusmann2012berufliche] with many leaving the profession within the first five years [@ingersoll2003]. Accordingly, when resources are lacking and coping fails, negative consequences for health (e.g., burnout) and for work (e.g., high turnover rates) can arise [@jalongo2006; @unterbrink2007; @aloe2014multivariate], highlighting the importance of professional expertise for managing teacher stress [@fisher2011].

@@

(2)	We further explored whether teaching experience made a difference in how teachers’ HR reacted to the classroom disruptions. We expected more experienced teachers to be less stressed by the classroom events (**Hypothesis 2a**).  In addition, we examined the relations between teachers’ subjective appraisals of the classroom events (specifically, the disruptiveness of the events, and their confidence in dealing with them) and teachers’ HR level, beyond the explanatory power of teaching experience. We expected higher HR levels for teachers who felt more disrupted, regardless of their teaching experience (**Hypotheses 2b**), and lower HR levels for teachers who felt more confident, regardless of teaching experience (**Hypothesis 2c**). We hypothesized that each of the three predictors (*teaching experience, disruption appraisal, confidence appraisal*) uniquely contributed to explaining variance in teachers’ HR levels (**Hypothesis 2d**). In addition, we exploratively ran analogous analyses for the *changes* in HR (i.e., slopes).

@@

Each participant came to the lab for a period of approximately two hours in total, and each participant underwent the same phases (see Fig. 2): In the *pre-teaching phase*, the experimenter welcomed the participants and helped them put on the fitness tracker. This was followed by a warm-up session to familiarize the participants with the laboratory setting and the class. This phase took about 10-15 minutes and participants spent this time mostly standing or slowly walking around. During the *teaching phase*, the participants held their self-prepared micro-teaching unit to a class of three trained actors who performed nine, potentially disruptive, classroom events (e.g., chatting with a neighbor, heckling, looking at the phone; see Table ## in the supplementary material for an overview and categorization of all events; and Figure \ref{fig.a2} in the supplementary material for a depiction of the laboratory setting of the micro-teaching unit). The topic and class level of the teaching unit could be freely chosen by the teachers with the only requirement that the unit had to be an introductory lesson, and had to consist of supervised individual work and / or frontal teaching. The micro-teaching unit lasted about 15-20 minutes. Participants spent this time mostly standing or slowly walking around. While teaching, participants wore eye-tracking glasses, and their lesson was video-recorded. After having completed the micro-teaching unit, in the *post-teaching phase*, participants filled in questionnaires for approximately 10-15 minutes: a brief computer-based survey of sociodemographic data (e.g., teaching experience, gender, studied school type, studied school subjects, extracurricular teaching activities), and a short knowledge test that was irrelevant to the
present study. In the *interview phase*,
```{=latex}
\begin{wrapfigure}{r}{0.5\textwidth}
  \centering
  \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
  \includegraphics[width=0.5\textwidth]{images/Timeline_smaller.pdf}
  \label{fig.2}
\end{wrapfigure}
```
\noindent
participants engaged in a Stimulated Recall Interview (SRI). During the SRI, participants sat in front of a computer monitor and watched the video of their own lesson from the ego perspective, as recorded through the eye-tracking glasses. The experimenter stopped the video each time one of the nine classroom events happened, and asked five open-ended, and three rating questions per event. Two of the rating questions are relevant to the present study: the disruption and the confidence appraisal ratings (see Measures). The interview lasted about 45-60 minutes. Finally, in the *end phase*, participants filled in another questionnaire irrelevant to the present study, which lasted about 10-15 minutes.

@@

@@

```
# Results

@@

\begin{table}[ht]
    \centering
    \caption{Mean HR (\textit{M}), standard deviations HR (\textit{SD}), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized).}
    \begin{tabularx}{\textwidth}{lXXXXX}
        \toprule
        Interval & \textit{M} HR & \textit{SD} HR & Min & Max \\
        \midrule
        Overall Course of 2h & 90.09/0.04\footnotemark[9] & 15.76/0.991 & 51/-4.03 & 164/4.56 \\
        Pre-teaching interval ($I_1$) & 96.28/0.48 & 14.11/0.88 & 56/-3.56 & 139/3.24 \\
        Teaching interval ($I_2$) & 100.80/0.85 & 16.23/0.77 & 63/-2.18 & 164/4.37 \\
        Post-teaching interval ($I_3$) & 93.61/0.27 & 14.01/0.76 & 60/-2.17 & 150/3.06 \\
        Interview interval ($I_4$) & 82.32/-0.72 & 11.85/0.74 & 51/-2.51 & 132/4.39 \\
        End interval ($I_5$) & 77.95/-1.07 & 11.14/0.57 & 50\footnotemark[10]/-2.68 & 120/2.96 \\
        \bottomrule
    \end{tabularx}
    \label{tab_1}

@@

```{=latex}
\begin{figure}[H]
  \centering
  \caption{Overall course of the HR with the unstandardized HR in BPM shown in Fig. 3a. and the z-standardized HR shown in Fig. 3b. for the planned 2-hour study.}
  \includegraphics[width=1\textwidth]{plots_publication/loess_plot_std_unstd_new.pdf}
  \label{fig.3}
\end{figure}
```

```{=latex}
\begin{figure}[H]
  \centering
  \caption{Distribution of the standardized heart rate means in the five intervals}
  \includegraphics[width=1\textwidth]{plots_publication/box_plot.pdf}
  \label{fig.4}
\end{figure}
```

@@

\begin{table}[ht]
    \centering
    \caption{Analysis (\textit{M, SD, p-values}) for the mean intercepts and the mean slopes for the five intervals.}
    \begin{tabularx}{\textwidth}{lXXXXXX}
        \toprule
        Interval  & \multicolumn{2}{c}{M (SD)} & \multicolumn{2}{c}{$p$} \\ & Intercept & Slope & Intercept & Slope \\
        \midrule
        (1) Pre-teaching interval & 0.052 (0.820) & 0.085 (0.133) & .57 & $< .05$ \\
        (2) Teaching interval & 1.025 (0.690) & -0.039 (0.108) & $< .05$ & $< .05$ \\
        (3) Post-teaching interval & 0.549 (0.547) & -0.060 (0.101) & $< .05$ & $< .05$ \\
        (4) Interview interval & -0.617 (0.614) & -0.022 (0.070) & $< .05$ & $< .05$ \\
        (5) End interval & -1.004 (0.500) & -0.012 (0.074) & $< .05$ & .14 \\
        \bottomrule
    \end{tabularx}
    \label{tab_2}
\end{table}

@@

@@

\begin{table}[h]
    \centering
    \caption{Correlations between mean standardized HR/mean slopes and the predictor variables of teaching experience (TE), disruption appraisal (DA), and confidence appraisal (CA) for the five intervals.}
    \begin{tabularx}{\textwidth}{lccccc}
        \toprule
        Variable & Pre-teaching & Teaching & Post-teaching & Interview & End \\
        & interval & interval & interval & interval & interval \\
        \midrule
        Teaching Experience & $- .17/ - .27^*$ & .11/-.02 & $- .04/-.03$ & $.24^*/-.20$ & .04/.11 \\
        Disruption Appraisal & $- .01/.16$ & $- .20/.08$ & .20/$- .14$ & $- .13/.01$ & .04/.12 \\
        Confidence Appraisal & $- .10/ - .18$ & .06/.09 & .04/$- .03$ & .09/$- .19$ & $- .07/.13$ \\
        \bottomrule \\
          Note. * $p < .05$.
    \end{tabularx}
    \label{tab_3}
\end{table}

@@

@@

\captionof{table}{Standardized regression coefficients of mean standardized heart rate and mean slopes predicted by teaching experience, disruption appraisal, and confidence appraisal for the five intervals.}

@@

plot_list_appendix <- list(
  `Preparation Phase` = list(name = "Pre-Teaching Interval", mod = mods$preparation, data = graph_data$preparation),
  `Teaching Phase` = list(name = "Teaching Interval", mod = mods$teaching, data = graph_data$teaching),
  `Post Teaching Phase` = list(name = "Post-Teaching Interval", mod = mods$post, data = graph_data$post),
  `Interview Phase` = list(name = "Interview Interval", mod = mods$interview, data = graph_data$interview),
  `End Phase` = list(name = "End Interval", mod = mods$end, data = graph_data$end)
) %>% 
  map(~ ggplot(data = .$data,
               mapping = aes(x = time,  # Use the appropriate 'x' value (like 'work_hrs' in the original)
                             y = heart_rate_std,  # Use the appropriate 'y' value (like 'inc')
                             group = ID)) +
        geom_line(mapping = aes(y = fitted(.$mod)),  # Line for fitted values from the model
                  color = "blue",  # Adjust color for clarity
                  size = 1) +  # Line thickness
        geom_point(alpha = 0.5, size = 0.5) +  # Points with transparency and size
        facet_wrap(~ ID, nrow = 8) +  # Arrange plots by 'ID'
        xlab('Time (in Seconds)') +  # X-axis label (similar to 'Arbeitsstunden pro Woche')
        ylab('Heart Rate (Standardized)') +  # Y-axis label (similar to 'Nettoeinkommen')
        scale_x_continuous(breaks = c(0, 5, 10)) +  # Customize x-axis breaks as needed
        #labs(title = .$name) +  # Title for each plot based on phase name
        theme_bw() + # Use a clean theme
        theme(text = element_text(family = "Times",
                                  size = 14)
              )
      )

@@

ggsave(preparation_plot,
       filename = "plots_publication/plot_preparation_appendix.pdf",
       width = 25,
       height = 30,
       units = "cm")

ggsave(teaching_plot,
       filename = "plots_publication/plot_teaching_appendix.pdf",
       width = 25,
       height = 30,
       units = "cm")

ggsave(post_teaching_plot,
       filename = "plots_publication/plot_post_teaching_appendix.pdf",
       width = 25,
       height = 30,
       units = "cm")

ggsave(interview_plot,
       filename = "plots_publication/plot_interview_appendix.pdf",
       width = 25,
       height = 30,
       units = "cm")

ggsave(end_plot,
       filename = "plots_publication/plot_end_appendix.pdf",
       width = 25,
       height = 30,
       units = "cm")

@@

```{=latex}
\newpage
\appendix
\section*{Appendix}

@@

@@

@@

\begin{table}[ht]
    \centering
    \caption{Classification of nine, typical classroom disruptions according to @lohmann2003schulern performed in the micro-teaching unit by actors.}
    \begin{tabularx}{\textwidth}{XXX}
        \toprule
        \textbf{Verbal disruptions} & \textbf{Physical disruptions} & \textbf{Lack of eagerness to learn} \\
        \midrule
        Heckling & Clicking pen & Looking at phone \\
        Chatting & Snipping hands & Drawing \\
        Whispering & Drumming hands & Head on table \\
        \bottomrule
    \end{tabularx}
    \label{tab.a1}
\end{table}

\begin{figure}[htbp]
  \centering
  \caption{Laboratory setting of the micro-teaching unit. Note. The setting included three actors as the class (left) and a teacher (participant, right).}
  \includegraphics[width=0.7\textwidth]{appendix_figure1.png}
  \label{fig.a1}
\end{figure}

\begin{figure}[htbp]
  \centering\caption{Laboratory setting of the interview. Note. The experimenter and participant watched the previously taught micro-teaching unit on video.}
  \includegraphics[width=0.7\textwidth]{appendix_figure2.png}
  \label{fig.a2}
\end{figure}

\begin{figure}[htbp]
  \centering
  \caption{Linear estimation of individual HR changes over time during the preparation phase for $N$ = 81 participants. Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
  \includegraphics[width=1\textwidth]{plots_publication/plot_preparation_appendix.pdf}
  \label{fig.a3}
\end{figure}

\begin{figure}[htbp]
  \centering
  \caption{Linear estimation of individual HR changes over time during the teaching phase for $N$ = 81 participants. Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
  \includegraphics[width=1\textwidth]{plots_publication/plot_teaching_appendix.pdf}
  \label{fig.a4}
\end{figure}

\begin{figure}[htbp]
  \centering
  \caption{Linear estimation of individual HR changes over time during the post-teaching phase for $N$ = 81 participants. Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
  \includegraphics[width=1\textwidth]{plots_publication/plot_post_teaching_appendix.pdf}
  \label{fig.a5}
\end{figure}

\begin{figure}[htbp]
  \centering
  \caption{Linear estimation of individual HR changes over time during the interview phase for $N$ = 81 participants. Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
  \includegraphics[width=1\textwidth]{plots_publication/plot_interview_appendix.pdf}
  \label{fig.a6}
\end{figure}

\begin{figure}[htbp]
  \centering
  \caption{Linear estimation of individual HR changes over time during the end phase for $N$ = 81 participants. Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
  \includegraphics[width=1\textwidth]{plots_publication/plot_end_appendix.pdf}
  \label{fig.a7}
\end{figure}
```

>>>>

The teaching profession is one of the most stressful professions, with teachers facing a host of stressors during their everyday work [@smith2000; @herman2020; @schult2014belastet]. To better understand mechanisms in teacher stress, there is a growing research interest in physiological measures such as heart rate (HR) as online measures of teachers’ stress during teaching [@karner2021teachers; @wettstein2020ambulatory]. For example, it has been shown that teacher-centered activities and typical classroom-related stressors increase teacher HR during teaching activities [@sperka1995; @scheuch1997psychophysische; @donker2018; @junker2021; @huang2022class]. However, previous studies have often relied on expensive and obtrusive electrocardiographs (ECG). Modern fitness trackers represent a non-invasive and convenient alternative [@ferguson2015].

@@

Physiologically, HR is regulated by the sympathetic and parasympathetic nervous systems [@pham2021]. An increase in sympathetic activity results in HR being sped up (“fight or flight” response) [@taelman2009influence]; whereas an increase in parasympathetic activity results in HR being slowed down (“rest and digest” response, @battipaglia2015). Stress or mental and physical strain directly increases HR [@custodis2014heart; @sachs2014]. Therefore, an increase in HR can be regarded as an indicator of increasing stress, and a decrease as an indicator of relaxation and ease [@kyriacou1978]. Thus, fitness trackers offer low-cost and unobtrusive access to psychological stress data.

@@

Figure \ref{fig.1} shows, in a simplified way, how classroom events affect teachers’ stress level, according to the adaptation of the Lazarus model to teacher stress proposed by @van2006stress: When potential stressors (e.g., classroom disruptions) occur during teaching (1), teachers intuitively judge how disruptive the event is in a primary appraisal (2). If potential stressors are judged as threatening, i.e., as actual stressors (3), teachers consider whether they have sufficient resources for coping with the stressors (4). Teachers utilize these resources in trying to cope with the stressors, e.g., by employing classroom management strategies (5). In cases when coping fails, stress ensues, often accompanied by physiological reactions like increased HR (6). As part of the coping process, and dependent on its outcomes, teachers re-evaluate the stressor (7).

As shown in Figure \ref{fig.1}, teachers’ primary and secondary appraisal as well as coping attempts are influenced by professional experience. As professional experience grows, teachers develop cognitive scripts for managing classroom events, resulting in more complex and problem-focused classroom management skills [@wolff2021classroom], and thus more effective coping and less stress. Empirically, classroom management skills and problem-focused coping styles are linked to fewer instances of emotional exhaustion [@maslach2001job; @clunies2008self]. Novices in the teaching profession, on the other hand, face considerable stress and often feel overwhelmed by the demands of teaching [@ophardt2017klassenmanagement; @wolff2015keeping; @klusmann2012berufliche] with many leaving the profession within the first five years [@ingersoll2003]. Accordingly, when resources are lacking and coping fails, negative consequences for health (e.g., burnout) and for work (e.g., high turnover rates) can arise [@jalongo2006; @unterbrink2007; @aloe2014multivariate], highlighting the importance of professional expertise for managing teacher stress [@fisher2011].

```{=latex}
\captionsetup[figure]{
    labelfont=bf,       % Figure label bold (not italic)
    labelsep=newline,      % Period after Figure label
    textfont=it,          % Italic font for the caption text
    font=small,           % Smaller font size for APA style
    justification=justified, % Left-justified captions, as per APA guidelines
    singlelinecheck=false % Avoid centering if the caption is single-line
}

\captionsetup[table]{
    labelfont=bf,        % Figure label bold (not italic)
    labelsep=newline,      % Period after Figure label
    textfont=it,          % Italic font for the caption text
    font=small,           % Smaller font size for APA style
    justification=justified, % Left-justified captions, as per APA guidelines
    singlelinecheck=false % Avoid centering if the caption is single-line
}

\begin{figure}[htbp]
  \caption{\\
  A model of teacher stress (adapted from van Dick 2006, p.37, modified by the authors)}
  \centering
  \includegraphics[width=1\textwidth]{images/Model_Teacher_Stress_adapted_new.pdf}
  \label{fig.1}
\end{figure}
```

@@

(2)	We further explored whether teaching experience made a difference in how teachers’ HR reacted to the classroom disruptions. We expected more experienced teachers to be less stressed by the classroom events (**Hypothesis 2a**).  In addition, we examined the relations between teachers’ subjective appraisals of the classroom events (specifically, the disruptiveness of the events, and their confidence in dealing with them) and teachers’ HR level, beyond the explanatory power of teaching experience. We expected higher HR levels for teachers who felt more disrupted, regardless of their teaching experience (**Hypothesis 2b**), and lower HR levels for teachers who felt more confident, regardless of teaching experience (**Hypothesis 2c**). We hypothesized that each of the three predictors (*teaching experience, disruption appraisal, confidence appraisal*) uniquely contributed to explaining variance in teachers’ HR levels (**Hypothesis 2d**). In addition, we exploratively ran analogous analyses for the *changes* in HR (i.e., slopes).

@@

Each participant came to the lab for a period of approximately two hours in total, and each participant underwent the same phases (see Figure \ref{fig.2}): In the *pre-teaching phase*, the experimenter welcomed the participants and helped them put on the fitness tracker. This was followed by a warm-up session to familiarize the participants with the laboratory setting and the class. This phase took about 10-15 minutes and participants spent this time mostly standing or slowly walking around. During the *teaching phase*, the participants held their self-prepared micro-teaching unit to a class of three trained actors who performed nine, potentially disruptive, classroom events (e.g., chatting with a neighbor, heckling, looking at the phone; see Table ## in the supplementary material for an overview and categorization of all events; and Figure \ref{fig.a2} in the supplementary material for a depiction of the laboratory setting of the micro-teaching unit). The topic and class level of the teaching unit could be freely chosen by the teachers with the only requirement that the unit had to be an introductory lesson, and had to consist of supervised individual work and / or frontal teaching. The micro-teaching unit lasted about 15-20 minutes. Participants spent this time mostly standing or slowly walking around. While teaching, participants wore eye-tracking glasses, and their lesson was video-recorded. After having completed the micro-teaching unit, in the *post-teaching phase*, participants filled in questionnaires for approximately 10-15 minutes: a brief computer-based survey of sociodemographic
```{=latex}
\begin{wrapfigure}[36]{r}{0.5\textwidth}
  \centering
  \caption{\\
  Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
  \includegraphics[width=0.5\textwidth]{images/Timeline_smaller.pdf}
  \label{fig.2}
\end{wrapfigure}
```
\noindent data (e.g., teaching experience, gender, studied school type, studied school subjects, extracurricular teaching activities), and a short knowledge test that was irrelevant to the present study. In the *interview phase*,
participants engaged in a Stimulated Recall Interview (SRI). During the SRI, participants sat in front of a computer monitor and watched the video of their own lesson from the ego perspective, as recorded through the eye-tracking glasses. The experimenter stopped the video each time one of the nine classroom events happened, and asked five open-ended, and three rating questions per event. Two of the rating questions are relevant to the present study: the disruption and the confidence appraisal ratings (see Measures). The interview lasted about 45-60 minutes. Finally, in the *end phase*, participants filled in another questionnaire irrelevant to the present study, which lasted about 10-15 minutes.

@@

# Results

@@

@@

\begin{table}[ht]
    \centering
    \caption{\\
    Mean HR (\textit{M}), standard deviations HR (\textit{SD}), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized).}
    \begin{tabularx}{\textwidth}{lXXXXX}
        \toprule
        Interval & \textit{M} HR & \textit{SD} HR & Min & Max \\
        \midrule
        Overall Course of 2h & 90.09/0.04\footnotemark[9] & 15.76/0.991 & 51/-4.03 & 164/4.56 \\
        Pre-teaching interval ($I_1$) & 96.28/0.48 & 14.11/0.88 & 56/-3.56 & 139/3.24 \\
        Teaching interval ($I_2$) & 100.80/0.85 & 16.23/0.77 & 63/-2.18 & 164/4.37 \\
        Post-teaching interval ($I_3$) & 93.61/0.27 & 14.01/0.76 & 60/-2.17 & 150/3.06 \\
        Interview interval ($I_4$) & 82.32/-0.72 & 11.85/0.74 & 51/-2.51 & 132/4.39 \\
        End interval ($I_5$) & 77.95/-1.07 & 11.14/0.57 & 50\footnotemark[10]/-2.68 & 120/2.96 \\
        \bottomrule
    \end{tabularx}
    \label{tab_1}

@@

```{=latex}
\begin{figure}[H]
  \centering
  \caption{\\
  Overall course of the HR with the unstandardized HR in BPM shown in Fig. 3a. and the z-standardized HR shown in Fig. 3b. for the planned 2-hour study.}
  \includegraphics[width=1\textwidth]{plots_publication/loess_plot_std_unstd_new.pdf}
  \label{fig.3}
\end{figure}
```

@@

\begin{table}[ht]
    \centering
    \caption{\\
    Analysis (\textit{M, SD, p}-values) for the mean intercepts and the mean slopes for the five intervals.}
    \begin{tabularx}{\textwidth}{lXXXXXX}
        \toprule
        Interval  & \multicolumn{2}{c}{M (SD)} & \multicolumn{2}{c}{$p$} \\ & Intercept & Slope & Intercept & Slope \\
        \midrule
        (1) Pre-teaching interval & 0.052 (0.820) & 0.085 (0.133) & .57 & $< .05$ \\
        (2) Teaching interval & 1.025 (0.690) & -0.039 (0.108) & $< .05$ & $< .05$ \\
        (3) Post-teaching interval & 0.549 (0.547) & -0.060 (0.101) & $< .05$ & $< .05$ \\
        (4) Interview interval & -0.617 (0.614) & -0.022 (0.070) & $< .05$ & $< .05$ \\
        (5) End interval & -1.004 (0.500) & -0.012 (0.074) & $< .05$ & .14 \\
        \bottomrule
    \end{tabularx}
    \label{tab_2}
\end{table}

@@

```{=latex}
\begin{figure}[H]
  \centering
  \caption{\\
  Distribution of the standardized heart rate means in the five intervals}
  \includegraphics[width=1\textwidth]{plots_publication/box_plot.pdf}
  \label{fig.4}
\end{figure}
```

@@

\begin{table}[h]
    \centering
    \caption{\\
    Correlations between mean standardized HR/mean slopes and the predictor variables of teaching experience (TE), disruption appraisal (DA), and confidence appraisal (CA) for the five intervals.}
    \begin{tabularx}{\textwidth}{lccccc}
        \toprule
        Variable & Pre-teaching & Teaching & Post-teaching & Interview & End \\
        & interval & interval & interval & interval & interval \\
        \midrule
        Teaching Experience & $- .17/ - .27^*$ & .11/-.02 & $- .04/-.03$ & $.24^*/-.20$ & .04/.11 \\
        Disruption Appraisal & $- .01/.16$ & $- .20/.08$ & .20/$- .14$ & $- .13/.01$ & .04/.12 \\
        Confidence Appraisal & $- .10/ - .18$ & .06/.09 & .04/$- .03$ & .09/$- .19$ & $- .07/.13$ \\
        \bottomrule \\
          Note. * $p < .05$.
    \end{tabularx}
    \label{tab_3}
\end{table}

@@

\newpage

@@

\captionof{table}{\\
Standardized regression coefficients of mean standardized heart rate and mean slopes predicted by teaching experience, disruption appraisal, and confidence appraisal for the five intervals.}

@@

plot_list_appendix <- list(
  `Preparation Phase` = list(name = "Pre-Teaching Interval", mod = mods$preparation, data = graph_data$preparation),
  `Teaching Phase` = list(name = "Teaching Interval", mod = mods$teaching, data = graph_data$teaching),
  `Post Teaching Phase` = list(name = "Post-Teaching Interval", mod = mods$post, data = graph_data$post),
  `Interview Phase` = list(name = "Interview Interval", mod = mods$interview, data = graph_data$interview),
  `End Phase` = list(name = "End Interval", mod = mods$end, data = graph_data$end)
) %>% 
  map(~ ggplot(data = .$data,
               mapping = aes(x = time,  # Use the appropriate 'x' value (like 'work_hrs' in the original)
                             y = heart_rate_std,  # Use the appropriate 'y' value (like 'inc')
                             group = ID)) +
        geom_line(mapping = aes(y = fitted(.$mod)),  # Line for fitted values from the model
                  color = "blue",  # Adjust color for clarity
                  size = 1) +  # Line thickness
        geom_point(alpha = 0.5, size = 0.5) +  # Points with transparency and size
        facet_wrap(~ ID, nrow = 8) +  # Arrange plots by 'ID'
        xlab('Time (in Minutes)') +  # X-axis label (similar to 'Arbeitsstunden pro Woche')
        ylab('Heart Rate (Standardized)') +  # Y-axis label (similar to 'Nettoeinkommen')
        scale_x_continuous(breaks = c(0, 5, 10)) +  # Customize x-axis breaks as needed
        #labs(title = .$name) +  # Title for each plot based on phase name
        theme_bw() + # Use a clean theme
        theme(text = element_text(family = "Times",
                                  size = 14)
              )
      )

@@

ggsave(preparation_plot,
       filename = "plots_publication/plot_preparation_appendix.pdf",
       width = 25,
       height = 29,
       units = "cm")

ggsave(teaching_plot,
       filename = "plots_publication/plot_teaching_appendix.pdf",
       width = 25,
       height = 29,
       units = "cm")

ggsave(post_teaching_plot,
       filename = "plots_publication/plot_post_teaching_appendix.pdf",
       width = 25,
       height = 29,
       units = "cm")

ggsave(interview_plot,
       filename = "plots_publication/plot_interview_appendix.pdf",
       width = 25,
       height = 29,
       units = "cm")

ggsave(end_plot,
       filename = "plots_publication/plot_end_appendix.pdf",
       width = 25,
       height = 29,
       units = "cm")

@@

```{=latex}
\appendix
\section*{Appendix}

@@

\setcounter{table}{0}

@@

\renewcommand{\thetable}{A\arabic{table}}

@@

\begin{table}[ht]
    \centering
    \caption{\\
    Classification of nine, typical classroom disruptions according to \cite{lohmann2003schulern} performed in the micro-teaching unit by actors.}
    \begin{tabularx}{\textwidth}{XXX}
        \toprule
        \textbf{Verbal disruptions} & \textbf{Physical disruptions} & \textbf{Lack of eagerness to learn} \\
        \midrule
        Heckling & Clicking pen & Looking at phone \\
        Chatting & Snipping hands & Drawing \\
        Whispering & Drumming hands & Head on table \\
        \bottomrule
    \end{tabularx}
    \label{tab.a1}
\end{table}

\begin{figure}[htbp]
  \centering
  \caption{\\
  Laboratory setting of the micro-teaching unit. Note. The setting included three actors as the class (left) and a teacher (participant, right).}
  \includegraphics[width=0.5\textwidth]{appendix_figure1.png}
  \label{fig.a1}
\end{figure}

\begin{figure}[htbp]
  \centering\caption{\\
  Laboratory setting of the interview. Note. The experimenter and participant watched the previously taught micro-teaching unit on video.}
  \includegraphics[width=0.5\textwidth]{appendix_figure2.png}
  \label{fig.a2}
\end{figure}

\begin{figure}[htbp]
  \centering
  \caption{\\
  Linear estimation of individual HR changes over time during the preparation phase for $N$ = 81 participants. Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
  \includegraphics[width=1\textwidth]{plots_publication/plot_preparation_appendix.pdf}
  \label{fig.a3}
\end{figure}

\begin{figure}[htbp]
  \centering
  \caption{\\
  Linear estimation of individual HR changes over time during the teaching phase for $N$ = 81 participants. Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
  \includegraphics[width=1\textwidth]{plots_publication/plot_teaching_appendix.pdf}
  \label{fig.a4}
\end{figure}

\begin{figure}[htbp]
  \centering
  \caption{\\
  Linear estimation of individual HR changes over time during the post-teaching phase for $N$ = 81 participants. Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
  \includegraphics[width=1\textwidth]{plots_publication/plot_post_teaching_appendix.pdf}
  \label{fig.a5}
\end{figure}

\begin{figure}[htbp]
  \centering
  \caption{\\
  Linear estimation of individual HR changes over time during the interview phase for $N$ = 81 participants. Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
  \includegraphics[width=1\textwidth]{plots_publication/plot_interview_appendix.pdf}
  \label{fig.a6}
\end{figure}

\begin{figure}[htbp]
  \centering
  \caption{\\
  Linear estimation of individual HR changes over time during the end phase for $N$ = 81 participants. Each plot illustrates the mean standardized HR values (y-axis) across 10 minutes (x-axis), with the black dots representing observed HR data points and the blue line showing the estimated linear trend.}
  \includegraphics[width=1\textwidth]{plots_publication/plot_end_appendix.pdf}
  \label{fig.a7}
\end{figure}

\newpage
```
